---
title: "Tanzania Tourism Classification"
author: "Boniface Kalong"
date: "6/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r ,message=FALSE}
library(dplyr)

train <- read.csv("Train.csv")
test <- read.csv("Test.csv")
```



```{r}
library(skimr)
skimr::skim(train)
```

```{r}
train[train==""]<- NA
test[test==""]<- NA
```


```{r}
library(visdat)
visdat::vis_dat(train)
```





```{r}
Train <- train%>%
  mutate(total = train$total_female+train$total_male)
Test <- test%>%
  mutate(total = test$total_female+test$total_male)
#x <- Train$travel_with
#for (i in x) {
#  if (is.na(x[i]) & Train$total == 1){
#    return("Alone")
#  }
#}
Test <- na.omit(Test)
Train<- na.omit(Train)

Train[!(Train$total ==0),]
Test[!(Test$total ==0),]

```
```{r}

cat_col_Train <- c( 'country', 'age_group', 'travel_with', 'purpose',
       'main_activity', 'info_source', 'tour_arrangement',
       'package_transport_int', 'package_accomodation', 'package_food',
       'package_transport_tz', 'package_sightseeing', 'package_guided_tour',
       'package_insurance', 'first_trip_tz', 'cost_category')
cat_col_Test <- c( 'country', 'age_group', 'travel_with', 'purpose',
       'main_activity', 'info_source', 'tour_arrangement',
       'package_transport_int', 'package_accomodation', 'package_food',
       'package_transport_tz', 'package_sightseeing', 'package_guided_tour',
       'package_insurance', 'first_trip_tz')
```


```{r}
library(CatEncoders)
cat_data_Train <- Train[cat_col_Train]
lenc <- sapply(Train[cat_col_Train],function(x) LabelEncoder.fit(x))
            for (i in cat_col_Train){
                 cat_data_Train[[i]] <- transform(lenc[[i]],Train[[i]])
            }
cat_data_Test <- Test[cat_col_Test]
lenc <- sapply(Test[cat_col_Test],function(x) LabelEncoder.fit(x))
            for (i in cat_col_Test){
                 cat_data_Test[[i]] <- transform(lenc[[i]],Test[[i]])
            }
```


```{r}

df_Train <- cbind(cat_data_Train,Train[c('Tour_ID','total_female', 'total_male','night_mainland','night_zanzibar')])

df_Test <- cbind(cat_data_Test,Test[c('Tour_ID','total_female', 'total_male','night_mainland','night_zanzibar')])

```

```{python}
cat_data_Train = r.df_Train
cat_data_Test = r.df_Test
Cat_df = pd.concat([cat_data_Train,cat_data_Test])
```

Also the plot of proportions confirms that the target variable is slightly unbalanced.

```{r}
library(ggplot2)
options(repr.plot.width=4, repr.plot.height=4)
ggplot(py$Cat_df, aes(x=cost_category))+geom_bar(fill="blue",alpha=0.5)+theme_bw()+labs(title="Distribution of Cost Category")
```

Now we have to check if the is any correlation between variables as machine learning algorithms assume that the predictor variables are independent from each others.

```{r}
library(corrplot)
df <- py$Cat_df
df <- df%>%select(-Tour_ID)
```
As shown by this plot, many variables are highly correlated with each others. Many methods perform better if highly correlated attributes are removed. The Caret R package provides the find Correlation which will analyze a correlation matrix of your data’s attributes report on attributes that can be removed. Because of much correlation some machine learning models could fail.

## Modelling Approach

### Modelling








